manuscript

### 2025-01-29 doc/Manuscript.qmd
Continue methods. Modeling section.

Capture-recapture sampling was conducted according to Pollock's [@pollock1982] robust design. Under the robust design, three primary survey periods occurred each summer from 2014 to 2018, each consisting of three consecutive survey days (secondary periods).

@@

>>>>

Capture-mark-recapture (CMR) sampling was conducted according to Pollock's [@pollock1982] robust design. Under the robust design, three primary survey periods occurred each summer from 2014 to 2018, each consisting of three consecutive survey days (secondary periods). **More needed?**

@@

We estimated survival probability, detection probability, recruitment of new frogs into the adult population, and adult population size for the Mossy Pond *R. sierrae* population using a site-specific Jolly-Seber CMR model implemented in a Bayesian framework with R statistical software [@R](v4.4.2). Our model was adapted from the mrmr R package [@joseph2019] (https://snarl1.github.io/mrmr/index.html), which was developed for the analysis of robust design CMR data collected from *R. sierrae* populations. The model represents a superpopulation of M individuals whose states (not recruited, alive, dead) and observations (detected, not detected) evolve through time, with any new frogs assumed to arise from local reproduction [@knapp2024]. We assessed model convergence via trace plots and Gelman–Rubin statistics (rhat).

Models copmpared with LOO cross-validation.
